---
title: "MSDRFars"
author: "Simon west"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
fig_caption: yes
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
##Introduction

This vignette provides a tutorial for the MSDRFars package. 

The MSDRFars package contains 5 functions that load, manipulate, summarize and plot data taken from the 
US National Highway Traffic Safety Administration's [Fatality Analysis Reporting System](https://www.nhtsa.gov/Data/Fatality-Analysis-Reporting-System-(FARS)). 

The functions are: (data loading) make_filename, fars_read, fars_read_years, (data summary) fars_summarize_years & (data plot) fars_map_state.

These function are contained in 3 files, fars_data_load.R, fars_summarize_data.r & fars_plot_data.r.

The package also contains raw data that can be imported by the data load functions. The data has been provided by Coursera: [Data](https://d3c33hcgiwev3.cloudfront.net/_e1adac2a5f05192dc8780f3944feec13_fars_data.zip?Expires=1524960000&Signature=NXHupBg-gcvZzp0GLhXufqChLvchI4-EJ9ixVfEN9NSk3SAKfTc0uhkYVBnZAcSXbxwicOVgl3T3zriG~CHVncI59bWZyYz0ys8tMfvI5VQmAvFeywBg8rzWsjxduRWDi7DaNGS8WLTyucTi3UT9SLNV0GRaiw0IndPcEFwgo-8_&Key-Pair-Id=APKAJLTNE6QMUY6HBC5A)
 
## Usage
The data associate with this package is held inst/extdata which will be /extdata when the package is installed. Set your working directory to be "current directory"/extdata once the MSDRFars package is installed to access the raw data fles.

### Using the data loading functions (make_filename, fars_read, fars_read_years)


```{r get filepath and set working directory, echo=FALSE}
#file_path <- system.file("extdata","accident_2013.csv.bz2", package = "MSDRFars")
#library(devtools)
#load_all(MSDRFars)
library(magrittr)

#setwd("/home/sam/Coursera/DataScience/MSDR/3_Building_R_Packages/MSDRFars")

```
 

```{r make_filename function, echo=TRUE}

#make_filename(2013)

```

```{r fars_read function, echo=TRUE}
#fars_read("accident_2013.csv.bz2")
```

```{r fars_read_years function, echo=TRUE}
#fars_read_years(c(2013:2015))
```


### Using the summary function (fars_summarize_years)


```{r fars_summarize_years, echo=TRUE}
#fars_summarize_years(c(2013:2015))
```

### Using the data plotting function (fars_map_state)
```{r fars_map_state, echo=TRUE, fig.cap = "Accident Plot for Florida 2014."}
#fars_map_state(12, 2014)
```



## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```
