---
title: "MSDRFars"
author: "Simon west"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
##Introduction

This vignette provides a tutorial for the MSDRFars package. 

The MSDRFars package contains 5 functions that load, manipulate, summarize and plot data taken from the 
US National Highway Traffic Safety Administration's [Fatality Analysis Reporting System](https://www.nhtsa.gov/Data/Fatality-Analysis-Reporting-System-(FARS)). 

The functions are: (data loading) make_filename, fars_read, fars_read_years, (data summary) fars_summarize_years & (data plot) fars_map_state.

These function are contained in 3 files, fars_data_load.R, fars_summarize_data.r & fars_plot_data.r.

The package also contains raw data that can be imported by the data load functions. The data has been provided by Coursera: [Data](https://d3c33hcgiwev3.cloudfront.net/_e1adac2a5f05192dc8780f3944feec13_fars_data.zip?Expires=1524960000&Signature=NXHupBg-gcvZzp0GLhXufqChLvchI4-EJ9ixVfEN9NSk3SAKfTc0uhkYVBnZAcSXbxwicOVgl3T3zriG~CHVncI59bWZyYz0ys8tMfvI5VQmAvFeywBg8rzWsjxduRWDi7DaNGS8WLTyucTi3UT9SLNV0GRaiw0IndPcEFwgo-8_&Key-Pair-Id=APKAJLTNE6QMUY6HBC5A)
 
## Usage
The data associate with this package is held inst/extdata which will be /extdata when the package is installed. Set your working directory to be "current directory"/extdata once the MSDRFars package is installed to access the raw data fles.

### Loading the raw data files (make_filename, fars_read, fars_read_years)


#```{r get filepath and set working directory}
#file_path <- system.file("extdata","accident_2013.csv.bz2", package = "MSDRFars")

#setwd(file_path)

#```
 

```{r make_filename function}

#make_filename(2013)

```

```{r fars_read function}
# fars_read("accident_2013.csv.bz2")
```

```{r fars_read_years function}
# fars_read_years(c(2013:2015))
```


### Using the summary function (fars_summarize_years)


```{r}
#fars_summarize_years(c(2013:2015))
```

### Plotting the data (fars_map_state)
```{r}
# fars_map_state(12, 2014)
```


## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
